### 2019-05-10 paper/paper.tex
WIP: dev vs. researcher

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{mathpazo}
\usepackage{graphicx}
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{apacite}

@@

The same state-dependence goes for continuous deployment as well; it cannot exist without continuous integration. There is also the implication that continuous delivery is a major part of continuous deployment. The distinguishing factor of continuous deployment versus continuous delivery is the extra step of an automated process of the deployment to production \cite[p. ~3911]{shahin_babar_zhu_2017}. For this to be possible, the software must be verified against a robust and fully automated collection of test suites, assuring with high confidence that the software works as it is intended to by design. Rod Cope, CTO of Rogue Wave Software says that companies that use continuous deployment can push hundreds or even thousands of releases into production per day \cite{stackify_2018}.

Software professionals, however, often get these three continuous software engineering practices confused or often times do not understand the deeper details that differentiate one from another. For example, Kofi Senaya, Director of Product from Clearbridge Mobile says "continuous Integration means that when [developers] are working on the same code, they are building and unit-testing it to prevent any integration problems" \cite{stackify_2018}. The first misunderstanding from Kofi is that he implies continuous integration only runs unit tests against the source code. Other levels of testing such as integration and system testing can also be implemented for continuous integration. The second misunderstanding is the implication that unit tests will cover all cases of integration functionality. There is a reason that integration tests exist, and that is for testing that module-to-module interaction works as intended. The third misunderstanding is stating that the developers are building and unit testing the software. The statement assumes that continuous integration is a manual process by which the developers partake in compiling and then running tests against the software. Kofi then goes on to say that "the code is verified by the automated build which allows teams to identify problems" \cite{stackify_2018}, which conflicts with the previous statement. It is clear that explaining the uniquity of these continuous software engineering practices is a challenge for software professionals.

An added layer of complexity that makes defining what it means to do continuous software engineering more difficult is the well-documented phenomena of software developers and software researchers non-collaboration.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{mathpazo}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{apacite}

@@

The same state-dependence goes for continuous deployment as well; it cannot exist without continuous integration. There is also the implication that continuous delivery is a major part of continuous deployment. The distinguishing factor of continuous deployment versus continuous delivery is the extra step of an automated process of the deployment to production \cite[p. ~3911]{shahin_babar_zhu_2017}. For this to be possible, the software must be verified against a robust and fully automated collection of test suites, assuring with high confidence that the software works as it is intended to by design. Rod Cope, CTO of Rogue Wave Software says that companies that use continuous deployment can push hundreds or even thousands of releases into production per day \cite{stackify_2018}. The intent behind continuous deployment is deliver a working product to customers as fast as possible, hence the heavy emphasis on automation. Upon asking a software architect about the practice, who chose not be to named, said, "let me put it this way, if I want a pony, then give me a damn pony. That's how simple it should be" (anonymous, personal communication, April 30, 2019). Although spoken quite metaphorically, the architect does get across the idea that if the continuous deployment system was built the way it was supposed to, a 'want' should in fact result in a ready-to-use product.

Software professionals, however, often get these three continuous software engineering practices confused or often times do not understand the deeper details that differentiate one from another. For example, Kofi Senaya, Director of Product from Clearbridge Mobile says "continuous Integration means that when [developers] are working on the same code, they are building and unit-testing it to prevent any integration problems" \cite{stackify_2018}. The first misunderstanding from Kofi is that he implies continuous integration only runs unit tests against the source code. Other levels of testing such as integration and system testing can also be implemented for continuous integration. The second misunderstanding is the implication that unit tests will cover all cases of integration functionality. There is a reason that integration tests exist, and that is for testing that module-to-module interaction works as intended. The third misunderstanding is stating that the developers are building and unit testing the software. The statement assumes that continuous integration is a manual process by which the developers partake in compiling and then running tests against the software. Kofi then goes on to say that "the code is verified by the automated build which allows teams to identify problems" \cite{stackify_2018}, which conflicts with the previous statement. It is clear that explaining the intricacies of these continuous software engineering practices is a challenge for software professionals.

An added layer of complexity that makes defining what it means to do continuous software engineering more difficult is the well-documented phenomena of non-collaboration between software developers and academic researchers. Computer scientist and software engineering professor, Jan Bosch, states that even the greatest developers in the software industry view top academic researchers as people who give insignificant learning value and the converse being true as well \cite[p. ~29]{bosch_2014}. In particular, top researchers do not believe that top developers contribute much to their body of research. The intrinsic difference between the developer and researcher is in how they view the value of software engineering. Developers by nature of their work are expected to produce software in a timely business-oriented manner, whereas researchers are focused on the insights that data analysis can accomplish.

There has been effort to bridge the gap between the two groups but this effort has been far from trivial.

% \begin{figure}[ht!]
% 	\begin{center}
% 		\includegraphics[width=.75\textwidth]{images/research.png}
% 	\end{center}
% 	\captionsetup{justification=centering}
% 	\caption{Success Factor Model for Academia-Industry Collaboration, Adapted from \protect\citeA[p. ~30]{bosch_2014}}
% 	\label{academia_industry}
% \end{figure}
